---
title: "NLS town-plan tiles"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NLS town-plan tiles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(leedstrams)
```

## Tile maths

The NLS town plan rasters are served as Web Mercator *XYZ tiles* at URLs like:

`https://mapseries-tilesets.s3.amazonaws.com/os/town-england/North/{z}/{x}/{y}.png`

The helpers in this package implement the standard XYZ tile maths.

Developer-only, one-off checks (including a deterministic XYZ round-trip) live
in `dev/tests.Rmd`.

## Getting tiles near a point

```{r}
z <- 20
hyde_park <- c(lon = -1.561482, lat = 53.814711)
tiles <- nls_tiles_near_lonlat(hyde_park["lon"], hyde_park["lat"], z = z, n_tiles = 4)
tiles
```

## Downloading and stitching tiles

Remote tile downloads are intentionally disabled in this vignette so it remains
cheap to build during `R CMD check`.

To try a small mosaic interactively, flip `eval = FALSE` to `eval = TRUE`.

```{r, eval = FALSE}
base_url <- "https://mapseries-tilesets.s3.amazonaws.com/os/town-england/North"

r_list <- Map(
  function(x, y) nls_tile_rast_zxy(base_url = base_url, z = z, x = x, y = y),
  tiles$x,
  tiles$y
)

mosaic <- terra::merge(terra::sprc(r_list))
terra::plotRGB(mosaic)
```
